---
title: "Car Analysis with Shiny"
author: "Dinh Tuan Phan"
date: "4/29/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning=FALSE)
defaultW <- getOption("warn") 
options(warn = -1) 

```


## Project Overview

This peer assessed assignment has two parts. In this project, I use the mtcars dataset.

- First, you will create a Shiny application and deploy it on Rstudio's servers. 

- Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

## Slide with Bullets

The shiny app plots the relationship between different inputs from the mtcars dataset.

- Load data


```{r cars, warning=FALSE,message=FALSE}
data('mtcars')
library(plotly)
```

- Summary data
```{r}
head(mtcars)
```



## Interactive Plot created with Plotly

```{r}
plot_ly(data=mtcars,x=~hp,y=~mpg,color = ~factor(cyl),
size=~wt,type="scatter",mode="markers")
```

## UI Code (ui.R file)

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}

library(shiny)
shinyUI(fluidPage(
    
    # Application title
    titlePanel("Car Analysis"),
    
    sidebarPanel(
        
        selectInput("variable", "Variable:", 
                    c("Miles per gallon" = "mpg",
                      "Distance" = "disp",
                      "Cylinder" = "cyl"))
    ),
    
    mainPanel(
        h3(textOutput("caption")),

        plotOutput("carPlot")
    )
))
```

## Server Code (server.R file)

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
data('mtcars')

library(shiny)
library(plotly)
shinyServer(function(input, output) {
    
    formulaText <- reactive({
        paste("hp vs ", input$variable)
    })
    
    output$caption <- renderText({
        formulaText()
    })
    output$carPlot <- renderPlot({
       ggplot(mtcars,aes_string(x='hp',y=input$variable, col='hp')) + geom_point()
    })
    
})
```
